\subsection{Definitions, Acronyms, and Abbreviations}
\subsubsection{Definitions}
	\begin{itemize}
		\item Account:\\ A profile that is associated with individual that will make use of, and or provide services to the system.
		\item Account Holder:\\ An individual that is the owner of a Account.
		\item Back End:\\ Includes the server, the communication with the client and the database management.
		\item Cloud:\\ A decentralized serves that is related to Back End functionality.
		\item End User:\\ The individual that will make use of the product.
		\item Front End:\\ This includes an Android user interface and a rudimentary interface on the Raspberry Pi.
		\item Invalid:\\ The medical term to describe a patient that is  incapacitated by illness or injury.
		\item Peripheral Device:\\  Physical equipment that interacts with, and or monitors the environment, and individuals respectively.
		\item System User:\\ The individual that will develop and maintain the product.
		\item Unsecure medium:\\ A medium that is susceptible to breaches that threaten client confidentiality, data availability and the integrity of the system.
	\end{itemize}
\subsubsection{Abbreviations}
	\begin{itemize}
		\item EUID: External Unique Identifier:\\ A unique number external to the system (i.e. third party systems) that uniquely identifies an user from said external system.
		\item IUID: Internal Unique Identifier:\\ A unique number internal to the system that uniquely identifies an user.
	\end{itemize}