%https://en.wikipedia.org/wiki/List_of_system_quality_attributes
\subsection{Software System Attributes}
//need to add some more ilities?

\subsubsection{Accessibility}
The end user application will provide a customizable color palette that enables high contrast overlays to aide slightly visually impaired users.

\subsubsection{Availability}
Persistent availability to the system and its functions will be guaranteed throughout its operational lifetime. Special precaution might be necessary when system updates are rolled out. Load balancing techniques can also improve tolerance to single points of failure.

\subsubsection{Compatibility}
The end user application will be fully compatible with Android devices that have a screen resolution of at least 800 x 480 pixels. The system will be compatible with a small subset of available medical devices on the market, that implements a common protocol.

\subsubsection{Failure Transparency}
The system will exhibit high failure transparency both in connection, and data persistency. The system will attempt to handle errors such that end users will only be informed if critical faults occurs. Errors will however be reported to system users.

\subsubsection{Interchangeability}
The system will allow front end peripheral devices to be interchanged, given that they provide equivalent functionality, and implement a common protocol.

\subsubsection{Interoperability}
The system will employ standardized, consistent and well documented protocols to maximize interface opaqueness, thus in turn will allow maximum interoperability with present and future systems.

\subsubsection{Maintainability}
The system will implement suitable design patterns to cope with a changing environment, correct defects, meet new requirements, and to make future maintenance easier. A robust testing environment will be setup to detect development stage errors. Error logging will be integrated into code to detect production stage errors.

\subsubsection{Security}
The system will guarantee security of the users' personal information by means of encrypted communications and storage. Administrator accounts will only have access to anonymized data such that personal information exposure is rendered impossible.