TODO: 
Add inheritance to img
remove addSubscriber option from patientManager


Follows is the description of each manager and the layout of the table that they will manage. It also discusses some of the specialized functions that they will provide.

databaseManager:

	This is the parent class and it established the connection with the database. In the case that the database does 		not exit it will create one. It will do the same for all the tables specified to be in the database.

patientManager:

	This manager will store the identification of the patients on the system. Each patient will be able to obtain a list of all the individuals subscribed to their data, they will also have the ability to remove unwanted subscribers.

	Patient Table:
		(Email, Password, Address, SubscriberPassword, PK(Username), Age, Weight, Height, Reason, SubscriberList) 

	Age: will be an Integer.
	Weight: will be a Double and will be measured in kilograms.
	Height: will be a Double and will be measured in metres
	SubscriberList: will be a set of unique subscriber emails.	
	
	
subscriberManager:

This manager will store all the subscribers or general users. They will be identified by their email address. They will also have the ability to subscribe to patients, in which case the relevant information will be added to both the subscriber's list of patients and the patient's list of subscribers.

	Subscriber Table:
		( PK(Email), Password, Relation, PatientList)
		
		PatientList: will be a set of unique patient usernames.	

patientDataManager:

This manager will have the functionality to retrieve patient data within a time span. The retrieveBetween function will preform this functionality and return a set containing an array of the patient data as well as the max, min and average value obtained during that time span.

	PatientData Table:
		(PK(PatientUsername), PK(DeviceID), PK(TimeStamp), value)
		
		value: can be a double or a set of information.
		
		
		
		
		