\subsubsection{Functional Requirements}

\begin{itemize}
\item RQ1: ReVA shall report data.
	\begin{itemize}
	\item RQ1.1: ReVA shall collect patient vitality data and store it in the cloud.
	\item RQ1.2: ReVA shall display real time data for each connected device.
	\item RQ1.3: ReVA shall display a patient's history of data for each device.
	\item RQ1.4: ReVA shall display statistical data for each device.
	\end{itemize}

\item RQ2: ReVA shall notify appropriate persons at appropriate times.
	\begin{itemize}
	\item RQ2.1: ReVA shall analyse data and notify appropriate people when certain conditions are violated.
	\item RQ2.2: ReVA shall keep a track of all notifications for the patient.
	\item RQ2.3: ReVA shall allow a user to see the past notifications.
	\end{itemize}
	
\item RQ3: ReVA shall manage users' accounts.
	\begin{itemize}
	\item RQ3.1: ReVA shall allow a person to register and subscribe to a single patient.
	\item RQ3.2: ReVA shall allow a person to log in and out of a particular account.
	\item RQ3.3: ReVA shall allow a person to manage his or her account information.
	\item RQ3.4: ReVA shall allow admin users to add or remove users as well as grant admin rights to users.
	\end{itemize}

\item RQ4: ReVA shall have an advice/emergency section.
	\begin{itemize}
	\item RQ4.1: ReVA shall have static advice to be consulted in an emergency.
	\item RQ4.2: ReVA shall allow a user to add or remove medical professionals' contact details.
	\end{itemize}
	
\item RQ5: ReVA shall be able to configure devices remotely.
\end{itemize}