The product that this systems requirements specification is describing is known as ReVA (Revolutionary Vitality Analyser).
ReVA is an IoT Homecare System meant to monitor bed-ridden patients in terms of certain vital measurements such as heart rate, blood pressure,
and temperature, to name but a few. ReVA analyses and collects real-time vitality data from the patient, stores it in a remote database, and
reports it (either as real-time data or historical statistics). ReVA is also capable of alerting caretakers and medical professionals if there 
are fluctuations from the patients norms, so as to facilitate quick medical responses if necessary.\\ \\ReVA is not meant to replace true medical 
care, but enhance it by simplifying the monitoring of patients and optimizing the response time in case of emergencies. As ReVA is a 
monitoring and reporting system, it is incapable of aiding a patient's recovery. As such, a caretaker is necessary for the ReVA system 
to be optimally utilised. ReVA may be used for any bed-ridden patients such as the elderly, injured, comatose, pregnant, or simply sick. As it 
is a system with small hardware and wireless, attachable sensors, ReVA is comfortable and easy to use, providing a stress free means to keep track 
of a patient without hindering much of their comfort with wires and constant check-ups.\\ \\ReVA is also meant to bring clarity to family members 
and reduce stress as they can always monitor the patient so long as the patient is attached to ReVA. ReVA is a dedicated and persistent 
system that will do its best to keep an eye on you and see you safely back to a healthy state. 
